Refinements for open automata

### 2021-08-10 2021-Refinement/paper/refinementarticle.tex
reflexivite

It  is  easy  to  show  that  the  refinement  is  reflexive  and  transitive,  so  it  is  a  preorder on the set of open automata.

>>>>

We will  show  that  the  refinement  is  reflexive  and  transitive,  so  it  is  a  preorder on the set of open automata.

\begin{lemma} The relation \(\wrel{}{}{H}\) is a preorder thus enables stepwise refinement.
\end{lemma}
The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $\mpar{R\mpar{s_1, s_2}} \mapsto $ to be $s_1= s_2$ and  and checking the above conditions, we can see that\\
